---
title: "VHSV_Species_Comp"
author: "Anna Conklyn"
date: "2023-12-05"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(ggplot2)
library(magrittr)
library(dplyr)
library(ggpubr)
library(plyr)
library(rstatix)
library(ggprism)
library(ggtext)
library(gt)

getwd()
```

# Chapter 3: VHSV PREVALENCE IN ROUND GOBIES VERSUS SYMPATRIC HOST SPECIES IN THE NEARSHORE FISH ASSEMBLAGE OF THE UPPER ST. LAWRENCE RIVER

## Contents:
  > 1. Contingency table for infection prevalence between host species & pairwise Fisher's exact tests for prevalence differences between host species
  > 2. Pairwise Kruskal–Wallis test for titer differences between host species
  > 3. Figures & Tables: summary table, prevalence barplots and titer boxplots between host species

## Data setup

```{r}
All_VHSV<-read_xlsx("~/GitHub/USLR_VHSV_Species/Peak_VHSV_2018-2022.xlsx", col_names = TRUE)

All_VHSV<- filter(All_VHSV, Year %in%  c("2020", "2021"))

Positve_Hosts<- filter(All_VHSV, Diagnosis == "Positive")

Pooled_Host_Titers<- subset(Positve_Hosts, (!is.na(Positve_Hosts[,"Titer-P"])))
Pooled_Host_Titers$Isolate<-"Pooled"
Pooled_Host_Titers %<>% mutate (logTiter=log10(`Titer-P`))
                        
Brain_Host_Titers<- subset(Positve_Hosts, (!is.na(Positve_Hosts[,"Titer-B"])))
Brain_Host_Titers$Isolate<- "Brain"
Brain_Host_Titers %<>% mutate (logTiter=log10(`Titer-B`))

All_Host_Titers<- rbind(Pooled_Host_Titers, Brain_Host_Titers)

```

# Tissue Comparisons
## Comparison of prevalence between tissue types and distribution (i.e., brain only, pooled only, both)

```{r}
library(tidyr)
All_VHSV_pooled<- All_VHSV %>% select(c(Species, `Titer-P`)) 
All_VHSV_pooled$`Titer-P` %<>% as.numeric()
All_VHSV_pooled<- All_VHSV_pooled %>% mutate(`Titer-P`=replace_na(`Titer-P`,0))
All_VHSV_pooled$Tissue_diagnosis<- ifelse(All_VHSV_pooled$`Titer-P`== 0, "negative", "positive")
All_VHSV_pooled$Tissue<- "pooled"
names(All_VHSV_pooled)[2] <- "Titer"

All_VHSV_brain<- All_VHSV %>% select(c(Species, `Titer-B`)) 
All_VHSV_brain$`Titer-B` %<>% as.numeric()
All_VHSV_brain<- All_VHSV_brain %>% mutate(`Titer-B`=replace_na(`Titer-B`,0))
All_VHSV_brain$Tissue_diagnosis<- ifelse(All_VHSV_brain$`Titer-B`== 0, "negative", "positive")
All_VHSV_brain$Tissue<- "brain"
names(All_VHSV_brain)[2] <- "Titer"

Tissue_diagnosis<- rbind(All_VHSV_pooled, All_VHSV_brain)
```

```{r}
#percentages of all tested fish
Totals<- as.data.frame(table(All_VHSV$Species))
colnames(Totals) <- c("Species", "Total")

Tissue_Summary<- as.data.frame(table(data=All_VHSV$Tissue, All_VHSV$Species))
colnames(Tissue_Summary) <- c("Tissue", "Species", "Freq")

Tissue_Summary<- merge(Tissue_Summary, Totals, by="Species")
Tissue_Summary$Perc<- (Tissue_Summary$Freq / Tissue_Summary$Total)*100
Tissue_Summary_1<- filter(Tissue_Summary, Tissue!="Negative")
Tissue_Summary_1$Tissue <- ordered(Tissue_Summary_1$Tissue, levels=c("Brain", "Pooled Organ", "Both"))
(Tissue_Plot_prevalence_All<- ggplot(Tissue_Summary_1, aes(x=Species, y=Perc, fill = Tissue)) + geom_col(position = "dodge", droplevels=FALSE, color = "black")+ theme(text = element_text(size = 12), legend.position = "bottom") + theme_classic() + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=232)", "Lepomis sp." = "Lepomis spp. \n (n=157)",  "Rock Bass" = "Rock Bass \n (n=311)", "Round Goby" =  "Round Goby \n (n=156)", "Yellow Perch" = "Yellow Perch \n (n=200)"))+ ylab("Percent (%) of all tested fish"))


#percentages of VHSV-positive fish
Totals<- as.data.frame(table(Positve_Hosts$Species))
colnames(Totals) <- c("Species", "Total")

Tissue_Summary<- as.data.frame(table(data=Positve_Hosts$Tissue, Positve_Hosts$Species))
colnames(Tissue_Summary) <- c("Tissue", "Species", "Freq")

Tissue_Summary<- merge(Tissue_Summary, Totals, by="Species")
Tissue_Summary$Perc<- (Tissue_Summary$Freq / Tissue_Summary$Total)*100
Tissue_Summary$Tissue <- ordered(Tissue_Summary$Tissue, levels=c("Brain", "Pooled Organ", "Both"))
(Tissue_Plot_prevalence_Positives<- ggplot(Tissue_Summary, aes(x=Species, y=Perc, fill = Tissue)) + geom_col(position = "dodge", droplevels=FALSE, color = "black")+ ylim(0,100) + theme_classic() + theme(text = element_text(size = 12), legend.position = "bottom") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ ylab("Percent (%) of positive fish"))

```

```{r}

LEP<- Tissue_diagnosis %>% filter (Species=="Lepomis sp.")
(Lep_table<- as.data.frame.matrix(table(LEP$Tissue, LEP$Tissue_diagnosis)))
(Lep_test<-pairwise_fisher_test(Lep_table, conf.int = TRUE))
chisq.test(Lep_table) #Not Significant

RG<- Tissue_diagnosis %>% filter (Species=="Round Goby")
(RG_table<- as.data.frame.matrix(table(RG$Tissue, RG$Tissue_diagnosis)))
(RG_test<-pairwise_fisher_test(RG_table, conf.int = TRUE))
chisq.test(RG_table) #Not Significant (P=0.05)

YP<- Tissue_diagnosis %>% filter (Species=="Yellow Perch")
(YP_table<-as.data.frame.matrix(table(YP$Tissue, YP$Tissue_diagnosis)))
(YP_test<-pairwise_fisher_test(YP_table, conf.int = TRUE))
chisq.test(YP_table) #Significant

BBH<- Tissue_diagnosis %>% filter (Species=="Brown Bullhead")
(BBH_table<- as.data.frame.matrix(table(BBH$Tissue, BBH$Tissue_diagnosis)))
(BBH_test<-pairwise_fisher_test(BBH_table, conf.int = TRUE))
chisq.test(BBH_table) #Significant

RB<- Tissue_diagnosis %>% filter (Species=="Rock Bass")
(RB_table<- as.data.frame.matrix(table(RB$Tissue, RB$Tissue_diagnosis)))
(RB_test<-pairwise_fisher_test(RB_table, conf.int = TRUE))
chisq.test(RB_table) #Not Signficant

```

# Comparison of titers between tissue types and distribution (i.e., brain only, pooled only, both)
```{r}
#All combined fish
All_Host_Titers$Distribution<-ifelse(All_Host_Titers$Tissue=="Both", "Both", "Single")
All_Host_Titers$Tissue <- ordered(All_Host_Titers$Tissue, levels=c("Brain", "Pooled Organ", "Both"))

All_Host_Titers %>% filter(Isolate=="Brain") %>% kruskal.test(logTiter ~ Distribution, p.adjust.method = "bonferroni") #Significant
All_Host_Titers %>% filter(Isolate=="Pooled") %>% kruskal.test(logTiter ~ Distribution, p.adjust.method = "bonferroni") #Significant
```
### Lepomis spp.
```{r}
LEP_titers<- All_Host_Titers %>% filter(Species=="Lepomis sp.")
LEP_titers$Isolate %<>% as.factor()
LEP_titers$logTiter %<>% as.numeric()

#Median test brain vs. pooled
wilcox.test(logTiter ~ Isolate, data = LEP_titers, exact = FALSE)
kruskal.test(logTiter~Isolate, data = LEP_titers) #Not Signifcant

#Median test both vs. single
wilcox.test(logTiter ~ Distribution, data = LEP_titers, exact = FALSE)
kruskal.test(logTiter~Distribution, data = LEP_titers) #Significant

#Plot
(Tissue_Plot_Titers<- ggplot(LEP_titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ theme(text = element_text(size = 12), legend.position = "bottom"))
```

### Round Goby
```{r}
RG_titers<- All_Host_Titers %>% filter(Species=="Round Goby")
RG_titers$Isolate %<>% as.factor()
RG_titers$logTiter %<>% as.numeric()

#Median test brain vs. pooled
wilcox.test(logTiter ~ Isolate, data = RG_titers, exact = FALSE)
kruskal.test(logTiter~Isolate, data = RG_titers) #Not Significant

#Median test both vs. single
wilcox.test(logTiter ~ Distribution, data = RG_titers, exact = FALSE)
kruskal.test(logTiter~Distribution, data = RG_titers) #Significant

#Plot
(Tissue_Plot_Titers<- ggplot(RG_titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ theme(text = element_text(size = 12), legend.position = "bottom"))
```

### Brown Bullhead
```{r}
BBH_titers<- All_Host_Titers %>% filter(Species=="Brown Bullhead")
BBH_titers$Isolate %<>% as.factor()
BBH_titers$logTiter %<>% as.numeric()

#Median test brain vs. pooled
wilcox.test(logTiter ~ Isolate, data = BBH_titers, exact = FALSE)
kruskal.test(logTiter~Isolate, data = BBH_titers) #Not Significant

#Median test both vs. single- Can't test, no fish had VHSV in both tissues
#wilcox.test(logTiter ~ Distribution, data = BBH_titers, exact = FALSE)
#kruskal.test(logTiter~Distribution, data = BBH_titers)

#Plot
(Tissue_Plot_Titers<- ggplot(BBH_titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ theme(text = element_text(size = 12), legend.position = "bottom"))
```

### Yellow Perch
``` {r}
YP_titers<- All_Host_Titers %>% filter(Species=="Yellow Perch")
YP_titers$Isolate %<>% as.factor()
YP_titers$logTiter %<>% as.numeric()

#Median test brain vs. pooled
wilcox.test(logTiter ~ Isolate, data = YP_titers, exact = FALSE)
kruskal.test(logTiter~Isolate, data = YP_titers) #Not Significant

#Median test both vs. single
wilcox.test(logTiter ~ Distribution, data = YP_titers, exact = FALSE)
kruskal.test(logTiter~Distribution, data = YP_titers) #Not Significant

#Plot
(Tissue_Plot_Titers<- ggplot(YP_titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ theme(text = element_text(size = 12), legend.position = "bottom"))
```

### Rock Bass
```{r}
RB_titers<- All_Host_Titers %>% filter(Species=="Rock Bass")
RB_titers$Isolate %<>% as.factor()
RB_titers$logTiter %<>% as.numeric()

#Median test brain vs. pooled
wilcox.test(logTiter ~ Isolate, data = RB_titers, exact = FALSE)
kruskal.test(logTiter~Isolate, data = RB_titers) #Not Significant

#Median test both vs. single
wilcox.test(logTiter ~ Distribution, data = RB_titers, exact = FALSE)
kruskal.test(logTiter~Distribution, data = RB_titers) #Not Significant

(Tissue_Plot_Titers<- ggplot(RB_titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ theme(text = element_text(size = 12), legend.position = "bottom"))
```


```{r}
#Combined all species in one plot
(Tissue_Plot_Titers<- ggplot(All_Host_Titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() + facet_wrap(~Species) +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=10)", "Lepomis sp." = "Lepomis spp. \n (n=22)",  "Rock Bass" = "Rock Bass \n (n=20)", "Round Goby" =  "Round Goby \n (n=82)", "Yellow Perch" = "Yellow Perch \n (n=34)"))+ theme(text = element_text(size = 14), legend.position = "bottom")+ theme_classic() + theme(text = element_text(size = 12), legend.position = "bottom") )


wilcox.test(logTiter ~ Isolate, data = All_Host_Titers, exact = FALSE) #Not Significant
wilcox.test(logTiter ~ Distribution, data = All_Host_Titers, exact = FALSE) #Not Significant

table(All_Host_Titers$Distribution)
kruskal.test(logTiter~Distribution, data = All_Host_Titers)

(Tissue_Plot_Titers<- ggplot(All_Host_Titers, aes(x=Distribution, y=logTiter, fill=Isolate)) + geom_boxplot() + ylim(0,8)  +
  ylab("log10(Titer) (N-gene \n copies per 50 ng RNA)") + scale_x_discrete(labels=c("Both" = "Both \n (n=142)", "Single" = "Single \n  (n=96)"))+ theme(text = element_text(size = 14), legend.position = "bottom")+ theme_classic() + theme(text = element_text(size = 12), legend.position = "bottom") + scale_fill_manual(values=c("grey", "white")) + theme_classic()+ theme(text= element_text(size = 20, color="black", face="plain"), legend.position = "bottom"))

ggsave("Tissue_Plot_Titers.jpeg", device="jpeg", plot=Tissue_Plot_Titers, path="C:/Users/ah2355/Documents/RGCompetence_JFishDiseases/Figures", dpi="retina", width = 12, height = 9)

```


# Contingency table for infection prevalence and pairwise Fisher's Exact tests for differences between host species

```{r}

#Difference between Lepomis species

Lepomis<- All_VHSV %>% filter (Species=="Lepomis sp.")
Lepomis$LEP_sp %<>% as.factor()
(Lep_table<- as.data.frame.matrix(table(Lepomis$`LEP_sp`, Lepomis$Diagnosis)))
names(dimnames(Lep_table))<-c("Species", "Diagnosis")

pairwise_fisher_test(Lep_table, conf.int = TRUE, alternative = "two.sided", p.adjust.method = "bonferroni")
chisq.test(Lep_table) #not significantly different prevalence detected
```
### Pairwise fisher test

```{r}
(Species_table<- as.data.frame.matrix(table(All_VHSV$Species, All_VHSV$Diagnosis)))
names(dimnames(Species_table))<-c("Species", "Diagnosis")

(Species_test<-pairwise_fisher_test(Species_table, conf.int = TRUE, alternative = "two.sided", p.adjust.method = "bonferroni"))
Species_test$p<- round(Species_test$p, digits = 2)
Species_test$p.adj<- round(Species_test$p.adj, digits = 2)
names(Species_test)[names(Species_test)=='p.adj.signif']<- 'p.adj.sig'

(Species_prevalence_test_table<- gt(Species_test)%>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels())%>%
  cols_width(everything() ~ px(100)))

#Species_prevalence_test_table %>% gtsave(filename="Species_prevalence_FisherTest.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")

```

# Summary table of prevalence across species

```{r, echo=FALSE}
Species_table$Total<-rowSums(Species_table)
Species_table$Prevalence<- (Species_table$Positive/Species_table$Total)
Species_table$Species<- row.names(Species_table)

Species_table$Prevalence<- round(Species_table$Prevalence, digits = 4)

(CI<- binom.cloglog(Species_table$Positive, Species_table$Total, conf.level = 0.95))
CI_Prev<- round ((CI[,5:6]), 4)
Species_table %<>% cbind(CI_Prev)

(Print_Host_table<- Species_table %>% gt(rowname_col = "Species") %>%
  tab_stubhead(label = "Species") %>%  cols_move_to_start(columns = "Positive") %>% fmt_percent(columns =  c("Prevalence", "lower", "upper")) %>%  cols_merge(
    columns = c("Prevalence", "lower", "upper"),
    pattern = "{1}<< ({2}, {3})>>") %>%
  cols_label(
    Prevalence = html("Prevalence % (95% CI)") ))

Print_Host_table %>% gtsave(filename="Species_prevalence_summary.docx", path="C:/Users/ah2355/Documents/RGCompetence_JFishDiseases/Figures")
```

## Calculate 95% CI
```{r}
library(binom)
(LEP_table_1<- as.data.frame.matrix(table(LEP$Tissue, LEP$Tissue_diagnosis)))
LEP_table_1$Species<- "Lepomis sp."
LEP_table_1$tissue<- rownames(LEP_table_1)

(RG_table_1<- as.data.frame.matrix(table(RG$Tissue, RG$Tissue_diagnosis)))
RG_table_1$Species<- "Round Goby"
RG_table_1$tissue<- rownames(RG_table_1)

(YP_table_1<- as.data.frame.matrix(table(YP$Tissue, YP$Tissue_diagnosis)))
YP_table_1$Species<- "Yellow Perch"
YP_table_1$tissue<- rownames(YP_table_1)

(RB_table_1<- as.data.frame.matrix(table(RB$Tissue, RB$Tissue_diagnosis)))
RB_table_1$Species<- "Rock Bass"
RB_table_1$tissue<- rownames(RB_table_1)

(BBH_table_1<- as.data.frame.matrix(table(BBH$Tissue, BBH$Tissue_diagnosis)))
BBH_table_1$Species<- "Brown Bullhead"
BBH_table_1$tissue<- rownames(BBH_table_1)

(Species_table_1<- rbind(LEP_table_1, RG_table_1, YP_table_1, RB_table_1, BBH_table_1))
Species_table_1$Total<- Species_table_1$negative + Species_table_1$positive
Species_table_1$Prevalence<- (Species_table_1$positive / Species_table_1$Total)*100

(CI<- binom.cloglog(Species_table_1$positive, Species_table_1$Total, conf.level = 0.95))
CI_Prev<- CI[,5:6] *100
Species_table_1 %<>% cbind(CI_Prev)

(Host_prev<- ggplot(data=Species_table_1) + geom_col(aes(x=Species, y=Prevalence, fill=tissue), position = "dodge", color="black", stat="identity") + ylim(0,100)+ theme_classic () + labs(x = "Species",  y = "Prevalence (%)")  + theme(text= element_text(size = 20, color="black", face = "plain"), legend.position = "bottom") + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=232)", "Lepomis sp." = "Lepomis spp. \n (n=157)",  "Rock Bass" = "Rock Bass \n (n=311)", "Round Goby" =  "Round Goby \n (n=156)", "Yellow Perch" = "Yellow Perch \n (n=200)")) + geom_errorbar(aes(Species, ymin = lower, ymax = upper, group=tissue), width = 0.2, position = position_dodge(0.9)) + labs(fill="Tissue") + scale_fill_manual(values=c("grey", "white"), labels=c("Brain", "Pooled")))

(Host_prev<- Host_prev +  stat_pvalue_manual(Species_test, xmin="group1", xmax = "group2", step.increase = 0.15, y.position = 50, label="p.adj.sig", hide.ns = TRUE, label.size = 7, bracket.size =  0.5))

ggsave("Host_prev.jpeg", device="jpeg", plot=Host_prev, path="C:/Users/ah2355/Documents/RGCompetence_JFishDiseases/Figures", dpi="retina", width = 12, height = 9)

```

### Prevalence barplots between host species

```{r}


(Host_prev<- ggplot(data=Species_table) + geom_col(aes(x=Species, y=Prevalence), fill="gray80", color="black", stat="identity") + ylim(0,100)+ theme_classic () + labs(x = NULL,  y = "Prevalence (%)")  + theme(text= element_text(size = 14)) + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=232)", "Lepomis sp." = "Lepomis spp. \n (n=157)",  "Rock Bass" = "Rock Bass \n (n=311)", "Round Goby" =  "Round Goby \n (n=156)", "Yellow Perch" = "Yellow Perch \n (n=200)")) + geom_errorbar(aes(Species, ymin = lower, ymax = upper), width = 0.2))

(Host_prev<- Host_prev +  stat_pvalue_manual(Species_test, xmin="group1", xmax = "group2", step.increase = 0.1, y.position = 60, label="p.adj.sig", hide.ns = TRUE, label.size = 8, bracket.size =  0.5))


#ggsave("Host_prevalence.jpeg", device="jpeg", plot=Host_prev, path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures", dpi="retina", width = 14, height = 9)

```


# Pairwise median titer- Kruskal-Wallis test with Dunn post-hoc comparisons with Bonferroni correction between host species

```{r, echo=FALSE}

#Test difference between lepomis species

Lepomis_titers<- All_Host_Titers %>% filter(Species=="Lepomis sp.")
Lepomis_titers$LEP_sp %<>% as.factor()
Lepomis_titers$logTiter %<>% as.numeric()

wilcox.test(logTiter ~ LEP_sp, data = Lepomis_titers, exact = TRUE)
kruskal.test(logTiter~LEP_sp, data = LEP_titers) #Significantly different median titer value between Lepomis species

ggplot(data=Lepomis_titers) + geom_boxplot(aes(LEP_sp, logTiter, fill=Isolate)) + ylim(0,8)  + labs( y="log10(Titer) (N-gene \n copies per 50 ng RNA)")  + scale_fill_manual(values=c("grey", "white")) + theme_classic()+ theme(axis.text= element_text(size = 14), legend.text = element_text(size = 14), axis.title = element_text(size = 18), title=element_text(size=22), legend.position = "bottom", legend.title = element_text(size = 14))  

```




```{r}
(All_Host_Titers %>% kruskal.test(logTiter ~ Species, p.adjust.method = "bonferroni"))
Host_Titers_test<- All_Host_Titers %>% dunn_test (logTiter~Species, p.adjust.method = "bonferroni")

Host_Titers_test$p<- round(Host_Titers_test$p, digits = 2)
Host_Titers_test$p.adj<- round(Host_Titers_test$p.adj, digits = 2)
Host_Titers_test$statistic<- round(Host_Titers_test$statistic, digits = 2)
names(Host_Titers_test)[names(Host_Titers_test)=='p.adj.signif']<- 'p.adj.sig'

(Species_titer_test_table<- gt(Host_Titers_test) %>%
  tab_style(
    style = cell_text(weight = "bold", size = 12),
locations = cells_row_groups(groups = everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", size = 12),
    locations = cells_column_labels())%>%
  cols_width(everything() ~ px(65)))

#Species_titer_test_table %>% gtsave(filename="Species_titer_DunnTest.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")
```

### Titer boxplots between host species

```{r, echo=FALSE}
Host_titer<-ggplot(data=All_Host_Titers) + geom_boxplot(aes(Species, logTiter, fill=Isolate)) + ylim(0,8)  + labs( y="log10(Titer) (N-gene \n copies per 50 ng RNA)")  + scale_fill_manual(values=c("grey", "white")) + theme_classic()+ theme(text= element_text(size = 20, color="black", face="plain"), legend.position = "bottom")+ scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=232)", "Lepomis sp." = "Lepomis spp. \n (n=157)",  "Rock Bass" = "Rock Bass \n (n=311)", "Round Goby" =  "Round Goby \n (n=156)", "Yellow Perch" = "Yellow Perch \n (n=200)"))   

(Host_titer<- Host_titer +  stat_pvalue_manual(Host_Titers_test, xmin="group1", xmax = "group2", step.increase = 0.075, y.position = 6, label="p.adj.sig", hide.ns = TRUE, label.size = 7, bracket.size =  0.5))

ggsave("Host_titer.jpeg", device="jpeg", plot=Host_titer, path="C:/Users/ah2355/Documents/RGCompetence_JFishDiseases/Figures", dpi="retina", width = 12, height = 9)
```

