---
title: "VHSV_Species_ZIG"
author: "Anna Conklyn"
date: "2023-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE, message = FALSE)

library(readxl)
library(ggplot2)
library(magrittr)
library(dplyr)
```

## Import data
```{r}
getwd()
All_Titers <- read_xlsx("Titers.xlsx", col_names = TRUE) %>% mutate(Titer = round(Titer))
All_Titers$logTiter<-as.numeric(All_Titers$logTiter)
```

# Chapter 3: VHSV PREVALENCE IN ROUND GOBIES VERSUS SYMPATRIC NATIVE HOST SPECIES IN THE NEARSHORE FISH ASSEMBLAGE OF THE UPPER ST. LAWRENCE RIVER

## Contents:
  > 1. Visualize zero-inflation
  > 2. Zero-inflated Gamma mixed-effects modeling 

## 1. Visualize zero-inflation

### All Titers
```{r}
ggplot(data=All_Titers, aes(Titer)) + geom_histogram() + facet_wrap(.~Species)
with(All_Titers, mosaicplot(table( Species, Titer == 0), shade = TRUE))
```

### Log-transformed Titers
```{r}
ggplot(data=All_Titers, aes(logTiter)) + geom_histogram()  + facet_wrap(.~Species)
ggplot(data=All_Titers, aes(Species, logTiter)) + geom_violin() + ggtitle("log viral loads - non-zero")
```


## 2. Zero-inflated Gamma mixed-effects modeling 

### Species main effect, site and year random

```{r}
require(glmmTMB)

Species_fit <- glmmTMB(Titer ~ Species  + (1 | Site*Year) + (1 | Year), 
               ziformula = ~ Species + (1 | Site) + (1 | Year), 
               family = ziGamma(link = "log"), 
               data = All_Titers)
summary(Species_fit)
```

### Diagnostics using DHARMa

```{r}
require(DHARMa)
Species_fit_residuals <- simulateResiduals(Species_fit)
plot(Species_fit_residuals)
```
