---
title: "VHSV_Species_ZIG"
author: "Anna Conklyn"
date: "2023-12-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE, message = FALSE)

library(readxl)
library(ggplot2)
library(magrittr)
library(dplyr)
library(DHARMa)
library(glmmTMB)
library(gt)
library(gtable)
library(gtsummary)
library(tidyr)
```


## Data setup

```{r}
All_VHSV<-read_xlsx("G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Peak_VHSV_2018-2022.xlsx", col_names = TRUE)

All_VHSV<- filter(All_VHSV, Year %in%  c("2020", "2021"))

Positve_Hosts<- filter(All_VHSV, Diagnosis == "Positive")

Pooled_Host_Titers<- subset(Positve_Hosts, (!is.na(Positve_Hosts[,"Titer-P"])))
Pooled_Host_Titers$Isolate<-"Pooled"
Pooled_Host_Titers %<>% mutate (logTiter=log10(`Titer-P`), Titer=`Titer-P`)
                        
Brain_Host_Titers<- subset(Positve_Hosts, (!is.na(Positve_Hosts[,"Titer-B"])))
Brain_Host_Titers$Isolate<- "Brain"
Brain_Host_Titers %<>% mutate (logTiter=log10(`Titer-B`), Titer=`Titer-B`)

Negatives<- filter(All_VHSV, Diagnosis == "Negative" )
Negatives$Isolate<-"None"
Negatives %<>% mutate (Titer=0) %<>% mutate (logTiter=log10(Titer))

All_Titers<- rbind(Pooled_Host_Titers, Brain_Host_Titers, Negatives)
drop<- c("PCR ID","Extraction Date", "qPCR date", "QTY-B", "QTY-P", "Titer-B", "Titer-P")
All_Titers<- All_Titers[ , ! names(All_Titers) %in% drop, drop=F]



Sites <- read_xlsx("G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Sites.xlsx", col_names = TRUE)

All_Titers<- All_Titers %>% inner_join(Sites, by=c('Site'='Bay', 'Year'='Year'))
All_Titers$RGCPUE %<>% as.numeric()
All_Titers$Temperature %<>% as.numeric()

```

# Chapter 3: VHSV PREVALENCE IN ROUND GOBIES VERSUS SYMPATRIC NATIVE HOST SPECIES IN THE NEARSHORE FISH ASSEMBLAGE OF THE UPPER ST. LAWRENCE RIVER

## Contents:
  > 1. Visualize zero-inflation
  > 2. Zero-inflated Gamma mixed-effects modeling 

## 1. Visualize zero-inflation

### All Titers
```{r}
ggplot(data=All_Titers, aes(Titer)) + geom_histogram() + facet_wrap(.~Species)
with(All_Titers, mosaicplot(table( Species, Titer == 0), shade = TRUE))
```

### Log-transformed Titers
```{r}
ggplot(data=All_Titers, aes(logTiter)) + geom_histogram()  + facet_wrap(.~Species)
ggplot(data=All_Titers, aes(Species, logTiter)) + geom_violin() + ggtitle("log viral loads - non-zero")
```


## 2. Zero-inflated Gamma mixed-effects modeling 
## Fixed effects

### Null model:
  > Zero-inflation model
      > Fixed Effects: null
      > Random Effects: null
  > Gamma model
      > Fixed Effects: null
      > Random Effects: null

```{r}

null <- glmmTMB(Titer ~ 1, 
               ziformula = ~ ., 
               family = ziGamma(link = "log"), 
               data = All_Titers)
summary(null)
plot(simulateResiduals(null))

null_Comp<- AIC(null)
null_Comp$AIC<- AIC(null)
null_Comp$ZInf<- "."
null_Comp$Gamma<- "1"
null_Comp$ZIRandom<- "null"
null_Comp$GRandom<- "null"
null_Comp %<>% as.data.frame()
null_Comp %<>% select(-1)
```


### Full model:
 > Zero-inflation model
      > Fixed Effects: Species, RGCPUE, Temp
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species, RGCPUE, Temp
      > Random Effects: null

```{r}

ZISRT_GSRT <- glmmTMB(Titer ~ Species + RGCPUE + Temperature, 
               ziformula = ~ Species + RGCPUE + Temperature , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZISRT_GSRT)
plot(simulateResiduals(ZISRT_GSRT))

ZISRT_GSRT_Comp<- AIC(ZISRT_GSRT)
ZISRT_GSRT_Comp$AIC<- AIC(ZISRT_GSRT)
ZISRT_GSRT_Comp$ZInf<- "ZISRT"
ZISRT_GSRT_Comp$Gamma<- "GSRT"
ZISRT_GSRT_Comp$ZIRandom<- "null"
ZISRT_GSRT_Comp$GRandom<- "null"
ZISRT_GSRT_Comp %<>% as.data.frame()
ZISRT_GSRT_Comp %<>% select(-1)
```


###  ZISRT - GSR
 > Zero-inflation model
      > Fixed Effects: Species, RGCPUE, Temp
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null

```{r}

ZISRT_GSR <- glmmTMB(Titer ~ Species + RGCPUE, 
               ziformula = ~ Species + RGCPUE + Temperature, 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZISRT_GSR)
plot(simulateResiduals(ZISRT_GSR))

ZISRT_GSR_Comp<- AIC(ZISRT_GSR)
ZISRT_GSR_Comp$AIC<- AIC(ZISRT_GSR)
ZISRT_GSR_Comp$ZInf<- "ZISRT"
ZISRT_GSR_Comp$Gamma<- "GSR"
ZISRT_GSR_Comp$ZIRandom<- "null"
ZISRT_GSR_Comp$GRandom<- "null"
ZISRT_GSR_Comp %<>% as.data.frame()
ZISRT_GSR_Comp %<>% select(-1)
```

###  ZISR - GSRT
 > Zero-inflation model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species, RGCPUE, Temp
      > Random Effects: null

```{r}

ZISR_GSRT <- glmmTMB(Titer ~ Species + RGCPUE + Temperature, 
               ziformula = ~ Species + RGCPUE , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZISR_GSRT)
plot(simulateResiduals(ZISR_GSRT))

ZISR_GSRT_Comp<- AIC(ZISR_GSRT)
ZISR_GSRT_Comp$AIC<- AIC(ZISR_GSRT)
ZISR_GSRT_Comp$ZInf<- "ZISR"
ZISR_GSRT_Comp$Gamma<- "GSRT"
ZISR_GSRT_Comp$ZIRandom<- "null"
ZISR_GSRT_Comp$GRandom<- "null"
ZISR_GSRT_Comp %<>% as.data.frame()
ZISR_GSRT_Comp %<>% select(-1)
```

### ZISR - GSR
 > Zero-inflation model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null

```{r}

ZISR_GSR <- glmmTMB(Titer ~ Species + RGCPUE, 
               ziformula = ~ Species + RGCPUE , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZISR_GSR)
plot(simulateResiduals(ZISR_GSR))

ZISR_GSR_Comp<- AIC(ZISR_GSR)
ZISR_GSR_Comp$AIC<- AIC(ZISR_GSR)
ZISR_GSR_Comp$ZInf<- "ZISR"
ZISR_GSR_Comp$Gamma<- "GSR"
ZISR_GSR_Comp$ZIRandom<- "null"
ZISR_GSR_Comp$GRandom<- "null"
ZISR_GSR_Comp %<>% as.data.frame()
ZISR_GSR_Comp %<>% select(-1)
```


### ZIS - GSR
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null

```{r}

ZIS_GSR <- glmmTMB(Titer ~ Species+ RGCPUE, 
               ziformula = ~ Species  , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR)
plot(simulateResiduals(ZIS_GSR))

ZIS_GSR_Comp<- AIC(ZIS_GSR)
ZIS_GSR_Comp$AIC<- AIC(ZIS_GSR)
ZIS_GSR_Comp$ZInf<- "ZIS"
ZIS_GSR_Comp$Gamma<- "GSR"
ZIS_GSR_Comp$ZIRandom<- "null"
ZIS_GSR_Comp$GRandom<- "null"
ZIS_GSR_Comp %<>% as.data.frame()
ZIS_GSR_Comp %<>% select(-1)
```

### ZISR - GS
 > Zero-inflation model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species
      > Random Effects: null

```{r}

ZISR_GS <- glmmTMB(Titer ~ Species, 
               ziformula = ~ Species + RGCPUE , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZISR_GS)
plot(simulateResiduals(ZISR_GS))

ZISR_GS_Comp<- AIC(ZISR_GS)
ZISR_GS_Comp$AIC<- AIC(ZISR_GS)
ZISR_GS_Comp$ZInf<- "ZISR"
ZISR_GS_Comp$Gamma<- "GS"
ZISR_GS_Comp$ZIRandom<- "null"
ZISR_GS_Comp$GRandom<- "null"
ZISR_GS_Comp %<>% as.data.frame()
ZISR_GS_Comp %<>% select(-1)
```


### ZIS-GS
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species
      > Random Effects: null
 
```{r}

ZIS_GS <- glmmTMB(Titer ~ Species, 
               ziformula = ~ Species , 
               family = ziGamma(link = "log"), 
               data = All_Titers)
summary(ZIS_GS)

plot(simulateResiduals(ZIS_GS))

ZIS_GS_Comp<- AIC(ZIS_GS)
ZIS_GS_Comp$AIC<- AIC(ZIS_GS)
ZIS_GS_Comp$ZInf<- "ZIS"
ZIS_GS_Comp$Gamma<- "GS"
ZIS_GS_Comp$ZIRandom<- "null"
ZIS_GS_Comp$GRandom<- "null"
ZIS_GS_Comp %<>% as.data.frame() 
ZIS_GS_Comp %<>% select(-1)
```

### ZIS-null
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: null
  > Gamma model
      > Fixed Effects: null
      > Random Effects: null
 
```{r}

ZIS_null <- glmmTMB(Titer ~ 1, 
               ziformula = ~ Species , 
               family = ziGamma(link = "log"), 
               data = All_Titers)
summary(ZIS_null)

plot(simulateResiduals(ZIS_null))

ZIS_null_Comp<- AIC(ZIS_null)
ZIS_null_Comp$AIC<- AIC(ZIS_null)
ZIS_null_Comp$ZInf<- "ZIS"
ZIS_null_Comp$Gamma<- "null"
ZIS_null_Comp$ZIRandom<- "null"
ZIS_null_Comp$GRandom<- "null"
ZIS_null_Comp %<>% as.data.frame() 
ZIS_null_Comp %<>% select(-1)
```



### ZIS-null
 > Zero-inflation model
      > Fixed Effects: null
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species
      > Random Effects: null
 
```{r}

null_GS <- glmmTMB(Titer ~ Species, 
               ziformula = ~ ., 
               family = ziGamma(link = "log"), 
               data = All_Titers)
summary(null_GS)

plot(simulateResiduals(null_GS))

null_GS_Comp<- AIC(null_GS)
null_GS_Comp$AIC<- AIC(null_GS)
null_GS_Comp$ZInf<- "null"
null_GS_Comp$Gamma<- "GS"
null_GS_Comp$ZIRandom<- "null"
null_GS_Comp$GRandom<- "null"
null_GS_Comp %<>% as.data.frame() 
null_GS_Comp %<>% select(-1)
```



```{r}
Fixed_comparisons<- rbind(null_Comp , ZISRT_GSRT_Comp, ZISRT_GSR_Comp, ZISR_GSRT_Comp, ZISR_GSR_Comp, ZIS_GSR_Comp, ZISR_GS_Comp, ZIS_GS_Comp, ZIS_null_Comp, null_GS_Comp)

gt(Fixed_comparisons, rowname_col = "AIC") %>% 
  tab_stubhead(label = "AIC")  %>%
  tab_style(
    style = cell_text(weight = "bold"),
locations = cells_row_groups(groups = everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels())%>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_stubhead()) %>%   gtsave(filename="Species_ZIG_Fixed.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")


summary(ZISR_GSR)


```


## Evaluate random effects

### ZISR-GSR-SY-SY
 > Zero-inflation model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site, Year
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site, Year

```{r}

ZISR_GSR_SY_SY <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site) + (1 | Year), 
               ziformula = ~ Species + RGCPUE + (1 | Site) + (1 | Year), 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZISR_GSR_SY_SY)
plot( simulateResiduals(ZISR_GSR_SY_SY))

ZISR_GSR_SY_SY_Comp<- AIC(ZISR_GSR_SY_SY)
ZISR_GSR_SY_SY_Comp$AIC<- AIC(ZISR_GSR_SY_SY)
ZISR_GSR_SY_SY_Comp$ZInf<- "ZISR"
ZISR_GSR_SY_SY_Comp$Gamma<- "GSR"
ZISR_GSR_SY_SY_Comp$ZIRandom<- "Site, Year"
ZISR_GSR_SY_SY_Comp$GRandom<- "Site, Year"
ZISR_GSR_SY_SY_Comp %<>% as.data.frame()
ZISR_GSR_SY_SY_Comp %<>% select(-1)
```


### ZIS-GSR-SY-SY
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: Site, Year
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site, Year

```{r}

ZIS_GSR_SY_SY <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site) + (1 | Year), 
               ziformula = ~ Species + (1 | Site) + (1 | Year), 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_SY_SY)
plot( simulateResiduals(ZIS_GSR_SY_SY))

ZIS_GSR_SY_SY_Comp<- AIC(ZIS_GSR_SY_SY)
ZIS_GSR_SY_SY_Comp$AIC<- AIC(ZIS_GSR_SY_SY)
ZIS_GSR_SY_SY_Comp$ZInf<- "ZIS"
ZIS_GSR_SY_SY_Comp$Gamma<- "GSR"
ZIS_GSR_SY_SY_Comp$ZIRandom<- "Site, Year"
ZIS_GSR_SY_SY_Comp$GRandom<- "Site, Year"
ZIS_GSR_SY_SY_Comp %<>% as.data.frame()
ZIS_GSR_SY_SY_Comp %<>% select(-1)
```

### ZIS-GSR-SY-S
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: Site, Year
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site

```{r}

ZIS_GSR_SY_S <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site), 
               ziformula = ~ Species + (1 | Site) + (1 | Year), 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_SY_S)
plot( simulateResiduals(ZIS_GSR_SY_S))

ZIS_GSR_SY_S_Comp<- AIC(ZIS_GSR_SY_S)
ZIS_GSR_SY_S_Comp$AIC<- AIC(ZIS_GSR_SY_S)
ZIS_GSR_SY_S_Comp$ZInf<- "ZIS"
ZIS_GSR_SY_S_Comp$Gamma<- "GSR"
ZIS_GSR_SY_S_Comp$ZIRandom<- "Site, Year"
ZIS_GSR_SY_S_Comp$GRandom<- "Site"
ZIS_GSR_SY_S_Comp %<>% as.data.frame()
ZIS_GSR_SY_S_Comp %<>% select(-1)
```

### ZIS-GSR-S-SY
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: Site
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site, Year

```{r}

ZIS_GSR_S_SY <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site) + (1 | Year), 
               ziformula = ~ Species + (1 | Site) , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_S_SY)
plot( simulateResiduals(ZIS_GSR_S_SY))

ZIS_GSR_S_SY_Comp<- AIC(ZIS_GSR_S_SY)
ZIS_GSR_S_SY_Comp$AIC<- AIC(ZIS_GSR_S_SY)
ZIS_GSR_S_SY_Comp$ZInf<- "ZIS"
ZIS_GSR_S_SY_Comp$Gamma<- "GSR"
ZIS_GSR_S_SY_Comp$ZIRandom<- "Site"
ZIS_GSR_S_SY_Comp$GRandom<- "Site, Year"
ZIS_GSR_S_SY_Comp %<>% as.data.frame()
ZIS_GSR_S_SY_Comp %<>% select(-1)

```


### ZIS-GSR-S-S
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: Site
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site

```{r}

ZIS_GSR_S_S <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site) , 
               ziformula = ~ Species + (1 | Site) , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_S_S)
plot( simulateResiduals(ZIS_GSR_S_S))

ZIS_GSR_S_S_Comp<- AIC(ZIS_GSR_S_S)
ZIS_GSR_S_S_Comp$AIC<- AIC(ZIS_GSR_S_S)
ZIS_GSR_S_S_Comp$ZInf<- "ZIS"
ZIS_GSR_S_S_Comp$Gamma<- "GSR"
ZIS_GSR_S_S_Comp$ZIRandom<- "Site"
ZIS_GSR_S_S_Comp$GRandom<- "Site"
ZIS_GSR_S_S_Comp %<>% as.data.frame()
ZIS_GSR_S_S_Comp %<>% select(-1)

```

### ZIS-GSR-n-S
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: null
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site

```{r}

ZIS_GSR_n_S <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site) , 
               ziformula = ~ Species , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_n_S)
plot( simulateResiduals(ZIS_GSR_n_S))

ZIS_GSR_n_S_Comp<- AIC(ZIS_GSR_n_S)
ZIS_GSR_n_S_Comp$AIC<- AIC(ZIS_GSR_n_S)
ZIS_GSR_n_S_Comp$ZInf<- "ZIS"
ZIS_GSR_n_S_Comp$Gamma<- "GSR"
ZIS_GSR_n_S_Comp$ZIRandom<- "null"
ZIS_GSR_n_S_Comp$GRandom<- "Site"
ZIS_GSR_n_S_Comp %<>% as.data.frame()
ZIS_GSR_n_S_Comp %<>% select(-1)

```

### ZIS-GSR-S-n
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: Site
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: null

```{r}

ZIS_GSR_S_n <- glmmTMB(Titer ~ Species + RGCPUE  , 
               ziformula = ~ Species + (1 | Site) , 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_S_n)
plot( simulateResiduals(ZIS_GSR_S_n))

ZIS_GSR_S_n_Comp<- AIC(ZIS_GSR_S_n)
ZIS_GSR_S_n_Comp$AIC<- AIC(ZIS_GSR_S_n)
ZIS_GSR_S_n_Comp$ZInf<- "ZIS"
ZIS_GSR_S_n_Comp$Gamma<- "GSR"
ZIS_GSR_S_n_Comp$ZIRandom<- "Site"
ZIS_GSR_S_n_Comp$GRandom<- "null"
ZIS_GSR_S_n_Comp %<>% as.data.frame()
ZIS_GSR_S_n_Comp %<>% select(-1)

```



### ZIS-GSR-S*Y-S
 > Zero-inflation model
      > Fixed Effects: Species
      > Random Effects: Site, Year
  > Gamma model
      > Fixed Effects: Species, RGCPUE
      > Random Effects: Site

```{r}

ZIS_GSR_S.Y_S <- glmmTMB(Titer ~ Species + RGCPUE + (1 | Site), 
               ziformula = ~ Species + (1 | Site* Year), 
               family = ziGamma(link = "log"), 
               data = All_Titers)

summary(ZIS_GSR_S.Y_S)
plot( simulateResiduals(ZIS_GSR_S.Y_S))

ZIS_GSR_S.Y_S_Comp<- AIC(ZIS_GSR_S.Y_S)
ZIS_GSR_S.Y_S_Comp$AIC<- AIC(ZIS_GSR_S.Y_S)
ZIS_GSR_S.Y_S_Comp$ZInf<- "ZIS"
ZIS_GSR_S.Y_S_Comp$Gamma<- "GSR"
ZIS_GSR_S.Y_S_Comp$ZIRandom<- "Site*Year"
ZIS_GSR_S.Y_S_Comp$GRandom<- "Site"
ZIS_GSR_S.Y_S_Comp %<>% as.data.frame()
ZIS_GSR_S.Y_S_Comp %<>% select(-1)
```





```{r}
library(sjPlot)
library(broom)
require("dotwhisker")
require("broom.mixed")
require("flextable")

random<- rbind(ZISR_GSR_SY_SY_Comp, ZIS_GSR_SY_SY_Comp, ZIS_GSR_SY_S_Comp, ZIS_GSR_S.Y_S_Comp, ZIS_GSR_S_SY_Comp, ZIS_GSR_S_S_Comp, ZIS_GSR_n_S_Comp, ZIS_GSR_S_n_Comp, ZIS_GSR_Comp)
gt(random, rowname_col = "AIC") %>% 
  tab_stubhead(label = "AIC")  %>%
  tab_style(
    style = cell_text(weight = "bold"),
locations = cells_row_groups(groups = everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels())%>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_stubhead()) %>% gtsave(filename="Species_ZIG_Random.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")


print(summary(ZIS_GSR_SY_S))
simulationOutput<- simulateResiduals(ZIS_GSR_SY_S)
plot(simulationOutput)
testZeroInflation(simulationOutput)

ZIS_GSR_SY_S_df<- tidy(ZIS_GSR_SY_S, conf.int = TRUE)
ZIS_GSR_SY_S_df <- transform(ZIS_GSR_SY_S_df,term=sprintf("%s.%s", component, term))
ZIS_GSR_SY_S_df$model<- ZIS_GSR_SY_S_df$component

ZIS_GSR_SY_S_df %<>% 
  filter(!grepl('(Intercept)', term))

ZIS_GSR_SY_S_df

dwplot(ZIS_GSR_SY_S_df) + theme_bw(base_size = 14) + xlab("Coefficient Estimate") + ylab("") +  scale_colour_grey() + theme(legend.position = "none")


```







