---
title: "VHSV_Species_Comp"
author: "Anna Conklyn"
date: "2023-12-05"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(ggplot2)
library(magrittr)
library(dplyr)
library(ggpubr)
library(plyr)
library(rstatix)
library(ggprism)
library(ggtext)
library(gt)

getwd()
```

# Chapter 3: VHSV PREVALENCE IN ROUND GOBIES VERSUS SYMPATRIC HOST SPECIES IN THE NEARSHORE FISH ASSEMBLAGE OF THE UPPER ST. LAWRENCE RIVER

## Contents:
  > 1. Contingency table for infection prevalence between host species & pairwise Fisher's exact tests for prevalence differences between host species
  > 2. Pairwise Kruskal–Wallis test for titer differences between host species
  > 3. Figures & Tables: summary table, prevalence barplots and titer boxplots between host species

## Data setup

```{r}
All_VHSV<-read_xlsx("Peak_VHSV_2018-2022.xlsx", col_names = TRUE)

All_VHSV<- filter(All_VHSV, Year %in%  c("2020", "2021"))

Positve_Hosts<- filter(All_VHSV, Diagnosis == "Positive")

Pooled_Host_Titers<- subset(Positve_Hosts, (!is.na(Positve_Hosts[,"Titer-P"])))
Pooled_Host_Titers$Isolate<-"Pooled"
Pooled_Host_Titers %<>% mutate (logTiter=log10(`Titer-P`))
                        
Brain_Host_Titers<- subset(Positve_Hosts, (!is.na(Positve_Hosts[,"Titer-B"])))
Brain_Host_Titers$Isolate<- "Brain"
Brain_Host_Titers %<>% mutate (logTiter=log10(`Titer-B`))

All_Host_Titers<- rbind(Pooled_Host_Titers, Brain_Host_Titers)

```

### 1. Contingency table for infection prevalence between host species and pairwise Fisher's Exact tests for differences between host species

```{r}

(Species_table<- table(All_VHSV$Species, All_VHSV$Diagnosis))
names(dimnames(Species_table))<-c(  "Species", "Diagnosis")
Species_table<-as.data.frame.matrix(Species_table)

(Species_test<-pairwise_fisher_test(Species_table, conf.int = TRUE, alternative = "two.sided", p.adjust.method = "bonferroni"))
Species_test$p<- round(Species_test$p, digits = 2)
Species_test$p.adj<- round(Species_test$p.adj, digits = 2)
names(Species_test)[names(Species_test)=='p.adj.signif']<- 'p.adj.sig'

(Species_prevalence_test_table<- gt(Species_test)%>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels())%>%
  cols_width(everything() ~ px(100)))

Species_prevalence_test_table %>% gtsave(filename="Species_prevalence_FisherTest.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")

```


### 2. Pairwise median titer- Kruskal-Wallis test with Dunn post-hoc comparisons with Bonferroni correction between host species
```{r, echo=FALSE}
(All_Host_Titers %>% kruskal.test(logTiter ~ Species, p.adjust.method = "bonferroni"))
Host_Titers_test<- All_Host_Titers %>% dunn_test (logTiter~Species, p.adjust.method = "bonferroni")

Host_Titers_test$p<- round(Host_Titers_test$p, digits = 2)
Host_Titers_test$p.adj<- round(Host_Titers_test$p.adj, digits = 2)
Host_Titers_test$statistic<- round(Host_Titers_test$statistic, digits = 2)
names(Host_Titers_test)[names(Host_Titers_test)=='p.adj.signif']<- 'p.adj.sig'

(Species_titer_test_table<- gt(Host_Titers_test) %>%
  tab_style(
    style = cell_text(weight = "bold", size = 12),
locations = cells_row_groups(groups = everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", size = 12),
    locations = cells_column_labels())%>%
  cols_width(everything() ~ px(65)))

Species_titer_test_table %>% gtsave(filename="Species_titer_DunnTest.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")
```

## 3. Figures & Tables

### Summary of prevalence rates

```{r, echo=FALSE}
Species_table$Total<-rowSums(Species_table)
Species_table$Prevalence<- (Species_table$Positive/Species_table$Total)*100
Species_table$Species<- row.names(Species_table)

Species_table$Prevalence<- round(Species_table$Prevalence, digits = 2)

(Print_Host_table<- Species_table %>% gt(rowname_col = "Species") %>%
  tab_stubhead(label = "Species") %>%  cols_move_to_start(columns = "Positive"))

Print_Host_table %>% gtsave(filename="Species_prevalence_summary.png", path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures")
```

### Prevalence barplots between host species

```{r}

Host_prev<- ggplot(data=Species_table) + geom_col(aes(Species, Prevalence)) + ylim(0,100)+ theme_classic () + labs(x = NULL,  y = "Prevalence (%)")  + theme(axis.text = element_text(size = 14), axis.title = element_text(size = 18), title=element_text(size=22)) + scale_x_discrete(labels=c("Brown Bullhead" = "Brown Bullhead \n (n=232)", "Lepomis sp." = "Lepomis sp. \n (n=157)",  "Rock Bass" = "Rock Bass \n (n=311)", "Round Goby" =  "Round Goby \n (n=156)", "Yellow Perch" = "Yellow Perch \n (n=200)"))

(Host_prev<- Host_prev +  stat_pvalue_manual(Species_test, xmin="group1", xmax = "group2", step.increase = 0.1, y.position = 60, label="p.adj.sig", hide.ns = TRUE, label.size = 8, bracket.size =  0.7))


ggsave("Host_prevalence.jpeg", device="jpeg", plot=Host_prev, path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures", dpi="retina", width = 14, height = 9)

```


### Titer boxplots between host species

```{r, echo=FALSE}
Host_titer<-ggplot(data=All_Host_Titers) + geom_boxplot(aes(Species, logTiter, fill=Isolate)) + ylim(0,8)  + labs( y="log10(Titer) (N-gene \n copies per 50 ng RNA)")  + scale_fill_manual(values=c("grey", "white")) + theme_classic()+ theme(axis.text= element_text(size = 14), legend.text = element_text(size = 14), axis.title = element_text(size = 18), title=element_text(size=22), legend.position = "bottom", legend.title = element_text(size = 14))  

(Host_titer<- Host_titer +  stat_pvalue_manual(Host_Titers_test, xmin="group1", xmax = "group2", step.increase = 0.1, y.position = 5.0, label="p.adj.sig", hide.ns = TRUE, label.size = 8, bracket.size =  0.7))

ggsave("Host_titer.jpeg", device="jpeg", plot=Host_titer, path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures", dpi="retina", width = 14, height = 9)
```


### Join plots 

```{r}
(VHSV_Species<- ggarrange(Host_prev, Host_titer, nrow = 2))
 ggsave("JOINED_VHSV_Species.jpeg", device="jpeg", plot=VHSV_Species, path="G:/Dissertation/Chapter 3- VHSV species/USLR_VHSV_Species/Figures", dpi="retina", width = 10, height = 14)
 
```


